---
title: "Acoustic Detections from Tidbits Exploratory Analysis"
author: "Sander Elliott"
format: pdf
editor: visual
---


```{r}
knitr::opts_chunk$set(warning = T, error = T, message = F, tidy = T)
options(tibble.width = Inf, tibble.print_max = Inf, tibble.print_min = Inf)
```

# Load Packages

GLATOS is a great package for acoustic telemetry work. It has to be installed via github. The code for that is commented out. I encourage looking through the glatos package in the help window.

```{r}
#install.packages("remotes")
#remotes::install_github("ocean-tracking-network/glatos")
library(glatos)
?glatos
library(tidyverse)
library(sf)
library(ggspatial)
library(ggmap)
```

# Load Data

I will load Atlantic sturgeon detections from 2016-2018 as an example. Export criteria are as follows:

Species: AST By Detection Dates Begin Date: 01/01/2016 End Date: 12/31/2018 Tag Type: Acoustic Export: Export Fish Histories Interval: 1 (Raw detections)

Exporting raw detections will take some time. It pulls the full fish history for every fish detected so you may get detections outside of your time frame. If Tidbits won't export try a shorter time frame and combine them later.


## Load Raw Detections adn write FST

### Load Tidbits download

Raw detections mess up github something fierce, so I will pull directly from my computer

```{r}
df <- read_csv( 
  "C:/Users/sander.elliott/Downloads/tidbits-export-1770136798454.csv", 
  show_col_types = FALSE)


bad <- problems(df)
bad
bad_rows <- df[bad$row, ]
unique(bad$col)
unique(bad$actual)
unique(bad_rows[,18])

rm(df); gc()

```

### Re-try df with rxid as character

```{r}
df2 <- read_csv(
  "C:/Users/sander.elliott/Downloads/tidbits-export-1770136798454.csv",
  col_types = cols(
    RxID = col_character()
  )
)


bad2 <- problems(df2)
bad2

unique(df2[,18])
glimpse(df2)
```


### Write FST to save space and remove huge df

```{r}
dim(df2)
names(df2)
names(df2)[1:10]
str(df2$Period)   # or whatever your time column is

str(df2$Period)
head(df2$Period, 10)

# optional drop
df2 <- df2 %>% select(-any_of(c("SensorType","avgSensorValue", "avgCompute", 
                              "Codespace", "AltFishID", "avgComputedValue", 
                              "Frequency", "avgPower", "AntennaID")))

write_fst(df2, "data/ASTdet16to18.fst")

rm(df2); gc()

rm(list = ls())
rm(list = ls(all.names = TRUE))

```

## Load FST

```{r}
det <- read.fst("data/ASTdet16to18.fst")
glimpse(det)
```

## Get to Work Fixing up Data

```{r}

```













